### 2015-06-09 LOI/inc2.tex
added a couple of sentences about 'negotiation' stuff. Didn't write exactly about 'negotiation' - The word sounds to me there is a handshake going on.

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment,
and allow for selectable data quality, by adjusting its accuracy and error, 
in order to meet the time or resource constraint. 
We will explore beyond the traditional high volume I/O pattern of
checkpoint/restart, and will address the challenges posed by other essential
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future DOE system with many of today's applications, including the
s XGC1, GTC, QMCPack, and SpecFM3D simulations.

@@

Our technical approach is based on the insight that storage system awareness
of application data requirements provides a powerful tool for guiding key
extreme scale challenges such as data access method,  data representation in
storage, and data
placement within the hierarchy.
%Our overall technical approach is based on an application-aware runtime
%realization of tradeoffs in data representation, data placement and data
%access. 
Towards this goal, we will allow users, both the developers of applications
and science users running these applications, 
 to plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, as well as data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto multiple storage tiers, and enable application-guided
data reductions/transformations to address capacity and bandwidth
bottlenecks. 
%
%Our approach can be most easily understood by considering a traditional
%  supermarket logistics problem. Given a limited amount of shelf space,
%  fluctuating user demands and priorities, and the need to optimize profit at
%  a market wide level instead of per product, the logistical problem combines
%  predictions about the variants and the indicated constraints to find a
%  solution. Self space is itself not a homogenous, with different locations
%  providing greater rewards to the placed items. Furthermore, haphazard
%  organization of items produces suboptimal results because it would ignore
%  locality in purchasing. Backroom and warehouses represent tiers of storage
%  where objects can be stored in bulk, but have a substantial overhead (and
%  thus lower utility) in access. Similar to this scenario, the data management
%  problem is a complex logistics problem. Shelf space is analogous to high
%  performance/lower capacity storage. Locality is an important consideration,
%  not just for single data objects but also through the identification of
%  domain meaningful relationships between objects. The tiers of the storage
%  hierarchy provide lower cost for data storage, but also increase the
%  overhead for access.
%
 For example, based on user and application insights into how the data is used,
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those with features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve if left unmanaged. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into the middleware and storage,
we will be able to selectively store data at different levels, and allow a user to select 
not only what data to retrieve but also specify an acceptable timeframe and accuracy.

>>>>

Our objective here is to reduce the time to knowledge, not just for a single
application, but for the entire workload in a multi-user environment, where
the storage is shared among users.
We achieve this goal by allowing selectable data quality, by trading its accuracy and error
in order to meet the time or resource constraint. 
We will explore beyond the traditional high volume I/O pattern of
checkpoint/restart, and will address the challenges posed by other essential
data access patterns in the knowledge gathering process.
Ultimately, we will take the knowledge from the storage system to provide vital feedback to the middleware 
so that the best possible decisions can be autonomically made between the user intentions and
the available system resources.  
We will test our prototypes  on current and future DOE system with many of today's applications, including the
s XGC1, GTC, QMCPack, and SpecFM3D simulations.

@@

Our technical approach is based on the insight that storage system awareness
of application data requirements provides a powerful tool for guiding key
extreme scale challenges such as data access method,  data representation in
storage, and data
placement within the hierarchy.
%Our overall technical approach is based on an application-aware runtime
%realization of tradeoffs in data representation, data placement and data
%access. 
Towards this goal, we will allow users, both the developers of applications
and science users running these applications, 
 to plug-in their knowledge 
about the data, represented not as bytes but as motifs, allowing the I/O and 
storage system to understand user
intentions, the relationships between data objects, as well as data access
and transport patterns. This will facilitate efficient mapping of data from
user space onto multiple storage tiers, and enable application-guided
data reductions/transformations to address capacity and bandwidth
bottlenecks. 
%
%Our approach can be most easily understood by considering a traditional
%  supermarket logistics problem. Given a limited amount of shelf space,
%  fluctuating user demands and priorities, and the need to optimize profit at
%  a market wide level instead of per product, the logistical problem combines
%  predictions about the variants and the indicated constraints to find a
%  solution. Self space is itself not a homogenous, with different locations
%  providing greater rewards to the placed items. Furthermore, haphazard
%  organization of items produces suboptimal results because it would ignore
%  locality in purchasing. Backroom and warehouses represent tiers of storage
%  where objects can be stored in bulk, but have a substantial overhead (and
%  thus lower utility) in access. Similar to this scenario, the data management
%  problem is a complex logistics problem. Shelf space is analogous to high
%  performance/lower capacity storage. Locality is an important consideration,
%  not just for single data objects but also through the identification of
%  domain meaningful relationships between objects. The tiers of the storage
%  hierarchy provide lower cost for data storage, but also increase the
%  overhead for access.
%
 For example, based on user and application insights into how the data is used,
we will offer a coarse grained, quick overview of a data set with progressively more detail in 
areas of interest such as those with features, and less detail in areas
without. These progressively more detailed data views require more storage
space and time to retrieve if left unmanaged. By defining mechanisms for applications to provide this 
knowledge and incorporating its awareness into the middleware and storage,
we will be able to selectively store data at different levels, and allow a user to select 
not only what data to retrieve but also specify an acceptable timeframe and accuracy.
On the other hand, the storage system layer may also dynamically 
adjust the level of data that will be retrieved
for an individual application, if that's allowed, to maximize the overall system efficiency and 
provide fairness among applications.
